A Domain Specific Language for SpectreGuard

### 2020-12-06 paper/main.tex
Abstract and syntax

% \documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}   %%%tc version
\documentclass[10pt, conference]{IEEEtran}
%\documentclass[conference,compsoc]{IEEEtran}
%\documentclass[10pt, conference]{IEEEtran}
%\documentclass[times, 10pt,onecolumn]{article}
\usepackage{amsmath, amssymb, enumerate}
\usepackage{semantic}

@@

@@

@@

Abstract goes here.

@@

\section{Background}
Cite a paper \cite{barroso2009datacenter}.

Cite multiple papers \cite{banga99resourcecontainers,barroso2009datacenter}

\section{Syntax}
...

@@

>>>>

% \documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}   %%%tc version
\documentclass[10pt, conference]{IEEEtran}
%\documentclass[conference,compsoc]{IEEEtran}
%\documentclass[10pt, conference]{IEEEtran}
%\documentclass[times, 10pt,onecolumn]{article}
\usepackage{amsmath, amssymb, enumerate}
\usepackage{semantic}
\usepackage{soul}
\usepackage{listings}

@@

\lstset{breaklines=true, basicstyle=\ttfamily\tiny, escapeinside={(*@}{@*)}}

@@

\setlength\extrarowheight{1.5pt}

@@

  A Spectre mitigation strategy in the form of a mechanism for marking variables as "non-speculative" was developed in
  \cite{SpectreGuard}. In this paper, we develop an embedded domain specific language (EDSL) in Haskell to provide
  support for this feature. The static type system of Haskell is used so that many basic forms of copying
  secret variables to public variables are disallowed. Additionally, a static analysis was developed which
  will detect some cases of secret variables leaking to public variables via control flow constructs.

@@

\section{Background}
Cite a paper. % \cite{barroso2009datacenter}.

Cite multiple papers. % \cite{banga99resourcecontainers,barroso2009datacenter}

\section{Syntax}
A correspondence between the syntax of the EDSL, which is inherited from
Haskell, and the C language is given in Fig. \ref{fig:Syntax}. In the right column, an
overline indicates that the transformation from EDSL to C is recursively
performed to the expression or command underneath the overline.

\begin{figure}[h]
\begin{tabular}{|l|l|}
  \hline
  EDSL syntax & C syntax \\
  \hline
  \begin{lstlisting}
  v <- decl x
  \end{lstlisting}
  & \begin{lstlisting}
  int v = x;
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  v <- allocPublic @Int n
  \end{lstlisting}
  & \begin{lstlisting}
  int v[n];
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  v <- allocPrivate @Int n
  \end{lstlisting}
  & \begin{lstlisting}
  int v[n] __attribute__((__nospec__));
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  arrA .= arrB
  \end{lstlisting}
  & \begin{lstlisting}
  memcpy(arrA, arrB, sizeof(arrA));
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  i .= j
  \end{lstlisting}
  & \begin{lstlisting}
  i = j;
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  arr ! i
  \end{lstlisting}
  & \begin{lstlisting}
  arr[i]
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  x <? y
  \end{lstlisting}
  & \begin{lstlisting}
  x < y
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  while cond body
  \end{lstlisting}
  & \begin{lstlisting}
  while ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{body}}$@*) }
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  if cond t f
  \end{lstlisting}
  & \begin{lstlisting}
  if ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{t}}$@*) } else { (*@$\overline{\ttt{t}}$@*) }
  \end{lstlisting}\\

  \hline
  \begin{lstlisting}
  for init (\i -> (cond, update, body))
  \end{lstlisting}
  & \begin{lstlisting}
  for (int i = (*@$\overline{\ttt{init}}$@*); (*@$\overline{\ttt{cond}}$@*); (*@$\overline{\ttt{update}}$@*))
    { (*@$\overline{\ttt{body}}$@*) }
  \end{lstlisting}\\

  \hline
\end{tabular}
\caption{Syntax of the EDSL vs C syntax}
\label{fig:Syntax}
\end{figure}

@@

A typing judgement is expressed with the syntax

\begin{equation*}
  \ttt{x :: $\beta$}
\end{equation*}

where \ttt{x} is some expression or command in the EDSL. This judgment means
that \ttt{x} has type $\beta$. This is the same syntax used by Haskell, and by extension
the EDSL, to explicitly specify a type in an expression.
